### 2017-01-17 robust-software.tex

FIXME: placeholder while renumbering.

Our focus in this short guide is on the software that is already built,
not on the process used to build it.
However,
we believe that version control is essential to sustainable software development
\cite{wilson2014,wilson2016}.

>>>>

Our focus in this short guide is on the software that is already built,
not on the process used to build it,
but we believe that version control is essential to sustainable software development
\cite{wilson2014,wilson2016}.
In particular,
developers will struggle to understand what they have actually built,
what it actually does,
and what they have actually released
without some mechanical way to keep track of changes.
They should therefore
\ruleminor{put everything created manually into version control as soon as it is created},
including programs, original field observations, and the source files for papers.
Files that can be regenerated at need,
such as the binaries for compiled programs or intermediate files generated during data analysis,
should not be versioned;
instead,
it is often more sensible to use an archiving system for them,
and store the metadata describing their contents in version control instead~\cite{noble2009}.
